Algomusicology, ???, Profit

### 2016-04-02 paper.tex
Talk more about lexicons.

Lexicons are interesting from a Kolmogorov complexity perspective, because they can be described concisely yet contain
multitudes. Paradoxically, lexicons display the property that the whole is simpler than (almost all of) the parts. That is,
the Kolmogorov complexity of all strings in our Library of Babel beyond a certain size are more complicated to describe
than the Library taken as a whole.

@@

Fortunately, there are other transcendental numbers that are more predictable. The Champernowne word is a constant whose
decimal expansion is the concatenation of the digits of the natural numbers.

>>>>

If we take the Kleene star of a particular alphabet, order the results countably, and then concatenate them, we get
a disjunctive sequence or lexicon. A lexicon has the property that every finite string is a substring.

The result of the Kleene star are interesting from a Kolmogorov complexity perspective, because they can be described
concisely yet contain multitudes. Paradoxically, it displays the property that the whole is simpler than (almost all of)
the parts. That is, the Kolmogorov complexity of one string in our Library of Babel is more complicated to describe
than the Library taken as a whole.

@@

If pi does have every possible of digits within its decimal expansion, then it's a disjunctive
sequence or lexicon. But we don't know for sure.

Fortunately, there are other transcendental numbers that are more predictable. The Champernowne word is a constant whose
decimal expansion is the concatenation of the digits of the natural numbers. The Champernowne word is definitively a lexicon,
which can be concluded by observing that it eventually contains any natural number. Any sequence of digits corresponds to
a natural number, so the word must contain all sequences of digits.

Of course, the sequence of digits may occur earlier too - the string "34" first occurs when the natural numbers three and
four are serialised, well before the natural number 34 is.
